`r spec$datasetname`

### 2025-06-13 report/template.qmd
Série brute -> Série CVS-CJO

rev_data <- lapply(basename(list_files), function(f){
    res <- lapply(studied_methods, function(method) {
        read.ts(file.path(dirname(params$file), spec$dataset, method, f), list = TRUE)[series]
    })
    c(list("Série brute" = lapply(all_data[[tools::file_path_sans_ext(f)]], window, 
                               start = min(sapply(spec_series, `[[`, "first_date")))),
      res)
})
names(rev_data) <- names(all_data)
rev_data <- rev(rev_data)
rev_data_ <- lapply(names(rev_data[[1]][[1]]), function(serie){
    res <- lapply(names(rev_data[[1]]), function(method){
        do.call(ts.union, lapply(rev_data, function(x){
            x[[method]][[serie]]
        }))
    })
    names(res) <- names(rev_data[[1]])
    res
})
names(rev_data_) <- names(rev_data[[1]][[1]])
rev_data <- rev_data_
rm(rev_data_)
```

>>>>

rev_data <- lapply(basename(list_files), function(f){
    res <- lapply(studied_methods, function(method) {
        read.ts(file.path(dirname(params$file), spec$dataset, method, f), list = TRUE)[series]
    })
    c(list("Série CVS-CJO" = lapply(all_data[[tools::file_path_sans_ext(f)]], window, 
                               start = min(sapply(spec_series, `[[`, "first_date")))),
      res)
})
names(rev_data) <- names(all_data)
rev_data <- rev(rev_data)
rev_data_ <- lapply(names(rev_data[[1]][[1]]), function(serie){
    res <- lapply(names(rev_data[[1]]), function(method){
        do.call(ts.union, lapply(rev_data, function(x){
            x[[method]][[serie]]
        }))
    })
    names(res) <- names(rev_data[[1]])
    res
})
names(rev_data_) <- names(rev_data[[1]][[1]])
rev_data <- rev_data_
rm(rev_data_)
```
